---
title: "Week 5 Assignment - Group 2"
output:
  pdf_document: default
  html_document: default
---

# Solutions:

In this file we implement the solutions of the questions that involve programming (Questions A, B). For more detailed explanations please see the attached word file.

First we import the relevant libraries:

```{r}
library(readxl)
library(forecast)
library(dplyr)
library(tidyverse)
library(lubridate)
library(padr)
library(tm)
library(rlist)
library(ggplot2)
library(SciViews)
```

Then we read the hourly prices for energy in excel file:

```{r}
data_orig <- read_excel("Week 5 Assignment data.xlsx")
data_orig
```

We make our dataset easier to use by deleting the first 5 rows and changing the column names:

```{r}
data_orig <- data_orig[-(1:5), ]
colnames(data_orig)<- c("timestamp","hour","price")
data_orig
```

### Question A

Then we need to find the average price of energy for every hour of the day, given the 56 days we have available.

```{r}
data_new <- mutate(data_orig, hour_day = rep(1:24, times=56))
data_new$price <-as.double(data_new$price)
by_hour <- group_by(data_new,hour_day)
mean_price <- summarise(by_hour, price_hour = mean(price,na.rm = TRUE))
data_new
```

The average price per hour is the following:

```{r}
mean_price
```

### Question B

We first define the decision variables:

```{r}
decision_variables <- mean_price
decision_variables$p <- 1
decision_variables$g <- 1
decision_variables$s <- 7*10^6

price <- decision_variables$price_hour
pump <- decision_variables$p
gen <- decision_variables$g
res <- decision_variables$s 
```

We now implement the optimisation function:

```{r}
profit.optim <- function(x, price){
  #assigning parameters
  bm <- x[1]
  ba <- x[2]
  Cm <- x[3]
  Ca <- x[4]
  Dm <- x[5]
  Da <- x[6]
  p <- x[7:30]
  g <- x[31:54]
  s <- x[55:78]
  price <- price
  #Calculations
  s[1]<- 5000000+14000*1*60
  for (t in 2:12){
    if (s[t-1]+bm*price[t-1]<=Cm){
      p[t]<-1
    }else{
      p[t]<-0
    } 
    if(s[t-1]+bm*price[t-1]>=Dm){
      g[t]<-1
    }else{
      g[t]<-0
    }
    s[t]<- 14000*p[t]*60-16000*g[t]*60+s[t-1]
  }
  for (t in 13:24){
    if (s[t-1]+ba*price[t-1]<=Ca){
      p[t]<-1
    }else{
      p[t]<-0
    } 
    if(s[t-1]+ba*price[t-1]>=Da){
      g[t]<-1
    }else{
      g[t]<-0
    }
    s[t]<- 14000*p[t]*60-16000*g[t]*60+s[t-1]
  }
  profit <- sum(g*270*price-p*300*price)
  return(profit)
}

dec_var <- c(500000,500000,6*10^6,8*10^6,6*10^6,8*10^6, pump, gen, res)
lower_bound <- c(-Inf, -Inf, 0, 0, 0, 0, rep(0,24), rep(0,24), rep(0,24)) 
upper_bound <- c(+Inf, +Inf, 10*10^6, 10*10^6, 10*10^6, 10*10^6, rep(1,24), 
                 rep(1,24), rep(10*10^6,23), 5000000) 
 
optim(x <- dec_var,fn = profit.optim, price = price, method="L-BFGS-B", 
      lower = lower_bound, upper = upper_bound, control = list(fnscale = -1))[1:2]
```

Hence, the maximum profit is $197,901.1$.
